Kindly Bent to Free Us

### 2019-06-17 kindly/motivation.tex
More examples.

\section{Hybrid programming styles}

@@

>>>>

\subsection{Hybrid programming style}

@@

\subsection{Type abstraction and linearity violation}

While linearity allows to verify many properties, it also prevents
the implementation of functions that are nevertheless safe. Rust addresses this
issue through the \lstinline/unsafe/ construct, which allows to locally
ignore linearity constraints. This is essential to build basic
functions such as splitting strings.
%
\lang allows to partially emulate this behavior using type abstraction
as provided by ML modules.
In particular, data types can be internally defined as unrestricted but exposed
as affine.

\TODO{Show example with arrays}

\subsection{Local data-structures with regions}

\TODO{Show a queue attached to a file}
